Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-05-07 WSSSPE2_report/WSSSPE2_review.tex
Section 2: A few minor edits. Section 3: format change only.

The review process was fairly standard. First, reviewers bid for papers. Then an
automated system matched the bids to determine assignments. After the reviewers
completed their assigned reviews (with an average of 4.9 reviews per paper and
4.1 reviews per reviewer), they used EasyChair\footnote{http://easychair.org/}
to record scores on relevance and comments. Finally, the organizers accessed the
information to decide which papers to associate with the workshop and provided
the comments to the authors to help them improve their papers.

@@

WSSSPE1 was organized into sessions, each of which was aimed at discussing one
or more of the themes from the call for papers, with a few paper authors invited
to summarize the other papers in them as a panel, followed by general discussion
about that theme. The mapping of papers to themes was done by the organizers.

@@

Finally, since some of the papers were not represented by cards in the process,
they were not placed in groups by the peer-grouping system; the authors of
these papers were asked which groups seemed the best for their papers---these
papers were then placed in those groups. Sections~\ref{sec:exploring}-\ref{sec:code_testing}
discuss the breakout groups, including a list of the papers associated with each
group.

@@

\subsection{Robert Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices~\cite{Downs_poster}}
Robert Downs, of the Columbia University Center for International Earth Science
Information Network (CIESIN),
%presented Community Recommendations for
%Improving Sustainable Scientific Software Practices (2014), and 
described a
focus group study conducted with %W. Christopher Lenhardt, Erin Robinson, Ethan
% Davis, and Nicholas Weber of 
the Science Software Cluster (SSC) of the Federation of Earth Science
Information Partners (ESIP). For the study, almost 300 attendees of the 2014
Summer ESIP Meeting were invited to participate in simultaneous roundtable
discussions on sustainability of science software. Over two-thirds of the
roundtable focus groups responded to a semi-structured survey that contained
three sets of questions eliciting recommendations for near-term actions of the
community to improve sustainable software practices. Initial analysis of the
participants' responses to the questionnaire revealed several suggestions, which
included improving community engagement and collaborative activities, increasing
understanding and awareness, and creating incentives to motivate sustainable
science software practices. The ESIP SSC plans to engage the community in the
recommended activities for improving sustainable scientific software practices.

>>>>

The review process was fairly standard. First, reviewers bid for papers. Then an
automated system matched the bids to determine assignments. After the reviewers
completed their assigned reviews (with an average of 4.9 reviews per paper and
4.1 reviews per reviewer), they used EasyChair\footnote{http://easychair.org/}
to record scores on relevance and comments. Finally, the organizers accessed the
information to decide which papers to associate with the workshop and provided
authors with the comments to help them improve their papers.

@@

WSSSPE1 was organized into sessions, each of which was aimed at discussing one
or more of the themes from the call for papers, with a few paper authors invited
to summarize the other papers in the session as a panel, followed by a general discussion
about that theme. The mapping of papers to themes was done by the organizers.

@@

Finally, since some of the papers were not represented by cards in the process,
they were not placed in groups by the peer-grouping system. The authors of
these papers were asked which groups seemed the best for their papers---these
papers were then placed in those groups. Sections~\ref{sec:exploring}-\ref{sec:code_testing}
discuss the breakout groups, including a list of the papers associated with each
group.

@@

\subsection{Robert Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices~\cite{Downs_poster}} Robert Downs, of the Columbia
University Center for International Earth Science Information Network (CIESIN),
described a focus group study conducted with the Science Software Cluster (SSC)
of the Federation of Earth Science Information Partners (ESIP). For the study,
almost 300 attendees of the 2014 Summer ESIP Meeting were invited to participate
in simultaneous roundtable discussions on sustainability of science software.
Over two-thirds of the roundtable focus groups responded to a semi-structured
survey that contained three sets of questions eliciting recommendations for
near-term actions of the community to improve sustainable software practices.
Initial analysis of the participants' responses to the questionnaire revealed
several suggestions, which included improving community engagement and
collaborative activities, increasing understanding and awareness, and creating
incentives to motivate sustainable science software practices. The ESIP SSC
plans to engage the community in the recommended activities for improving
sustainable scientific software practices.
